Integrating brain and biomechanical models - a new paradigm for understanding neuro-muscular control

### 2017-12-04 papers/integration/omm_integ.tex
More work in progress towards the post-review re-draft

The aim of this study was to demonstrate the importance of modelling
neurological systems \e{in concert with} the biomechanical systems
with which they have evolved. We hypothesised that by
combining existing neurophysiological models with an accurate model of
a musculo-skeletal system, and then `closing the loop' by allowing the
movements of the virtual muscles to modulate sensory feedback to the
brain model, shortcomings in the constituent models would be revealed,
leading to new knowledge.
%
\rvw{We call this closed-loop approach \e{computational
neurobehaviour}, meaning a complete, behaving model, with attention
paid to the biological accuracy of each brain and biomechanical
sub-system. There already exist many closed-loop \e{robotic} systems which
receive sensory input from the world, process that input and generate
behaviour by activating motor
systems
\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
now consider whether robotic systems which model biological
components \e{in hardware} could fall within our new category.
%
Using a number of examples, we will attempt to illustrate what we mean
by computational neurobehaviour. We'll consider which examples fall
into the new category and which are covered by other fields of
robotics or computational neuroscience. We will then attempt to
provide a definition of computational neurobehaviour.}

\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
biomimetic whisker sensory system, along with a biomimetic neural
system imitating the behaviour of the rat's sensory processing systems
and controlling the movement of the robot. \cite{fend_artificial_2004}
is a similar, wheeled, whiskered robot, with a repertoire of three
behaviours organised in a subsumption architecture. In both robots,
actions that are selected within the brain model drive a
non-biologically accurate wheel motor control algorithm to achieve
rotational and translational movements. Although both have
sensory and processing systems which are guided by biology, the
non-biological motor control stage prevents us from considering these
as being studies of computational neurobehaviour.}
%
\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
whose motor system closely resembles that of the real fish. The robot
is able to operate in a closed-loop mode, where sensory input is
provided to the non-biomimetic control algorithms from overhead
cameras, but its control system is also able to operate in open-loop
mode. Neither the control system, nor the sensory system are
biophysically accurate and we would not describe this study as
computational neurobehaviour. Nevertheless, the biophysically accurate
motor system could certainly form part of a computational
neurobehavioural study of swimming behaviour in the fish, if it were
combined with suitable sensory input and sensory processing models.}
%
\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
arm controlled via a dynamic neural field brain model. The sensory
input for this system---its `eyes'---is a Microsoft Kinect sensor; it
also has somatosensory feedback from the fingers of the robot's
hand. The neural field `brain' controls the seven degrees of freedom
of the arm to carry out the reach-and-grasp action. While this robot
has closed-loop control and is clearly inspired by biology, it remains
a study of robotics and of the improvement of the control of the
robot's reach-and-grasp function, rather than a study which aims to
learn more about the biology of a primate arm. For this reason, we
would describe the study of \cite{knips_neural_2017} as embodied
robotics or neuro-robotics.}
%
\rvw{\cite{arena_motor-skill_2017} describes a
robotic insect system based on the fly species \e{Drosophila
Melanogaster}. It has biomimetic insect legs implemented in a virtual
robot and a neuro-mimetic brain. Closing the loop is a visual sensory
input system which is able to determine the distance between the robot
and an obstacle and the obstacle's height. The visual system is not
described in detail and may not be biologically modelled (much in the
way that the visual processing stream is not modelled in detail in the
present work). Nevertheless, this study may reasonably be described as
compuational neurobehaviour; the authors demonstrate that the virtual
robot is able to learn to climb obstacles in a realistic manner and
suggest that the model may be compared with experimental data from
future Drosophila experiments addressing obstacle climbing and
learning.}

\rvw{To summarise, we give a definition of computational
neurobehaviour as \e{the study of biological sensory-motor system
behaviour using biophysically accurate models of sensory input, brain
and motor sub-systems operating in a closed-loop}. The sub-system
models may be implemented in software or hardware, provided that they
attempt to reproduce and explain features of the biological
sub-system.}

@@

% Reviewer 1's point 2.
\rvw{Address reviewer's question of ``whether inaccuracies in the
biomechanical model may introduce
errors that propagate through the closed loop system and cannot be
counteracted by the nervous system part of the simulation. How can you
(or someone using this or related models) exclude introducing
(biomechanical) properties that are not present in the biological
system, or make sure to not miss critical biomechanical properties
that might help remedy some of the shortcomings of the closed loop
model?''.}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/ccg_model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
fields (FEF), thalamus (THAL) and superior colliculus (SC). The
retinal input is presented via non-biologically plausible retinal
populations. The loops through basal ganglia, which define the
architecture, are shown with coloured lines: the cortical loop
(through FEF and THAL) in green and the sub-cortical loop (through SC
and THAL) in blue. Connections with arrowheads indicate excitatory
connections, those with circles are inhibitory. A red border indicates
that the box represents a sub-system of two or more populations; a
black box indicates (at least, within the context of the model) a
single neural population. The BG box is expanded in: \bol{b) The basal
ganglia model component.}
%
This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
subthalamic nucleus (STN), globus pallidum externum (GPe) and
substantia nigra reticulata (SNr). The model has three action channels
shown as black boxes within each blue population border. Three
channels of cortical input to the BG are also depicted. Red indicates
the activation level of a given channel, helping to illustrate the
selection mechanism. For example, the channel indicated by the
leftmost bar has a high salience (cortical input) and excites activity
in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
projection from STN is equivalent to summing its projections
channel-wise, and then projecting the sum to all channels of its
target populations (the blue arrows indicate that all channels of GPe
and SNr are targeted by the connection). Dopaminergic modulation of
the inputs to the striatum are indicated by the blue circles labelled
`d' and the dotted lines. The SNr sends inhibitory output projections
to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
connectivity pattern is based on the horizontal distance between the
location of a neural element in one layer, and the location of a
target neural element in the target layer for the connection. The
potential weight of the connection is given by a 2D Gaussian function,
which is maximum for the target neuron which exactly corresponds to
the source neuron, and drops down for target neurons which are
horizontally displaced from the source neuron. A threshold is applied
to avoid a computationally expensive all-to-all connectivity (with
most of these connections having negligible weight values).  If the
weight is non-zero, then a connection is made from source to target,
otherwise no connection is made. \bol{d) Gaussian connectivity.} This
image shows connectivity (green rays) from two source neurons (in
Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
circular connectivity pattern is seen. This does not show the weights,
which reduce `towards the edge of the circle' and follow the
relationship shown in (c).}
\end{figure}

>>>>

The aim of this study was to demonstrate the importance of modelling
neurological systems \e{in concert with} the biomechanical systems
with which they have evolved. We hypothesised that by
combining existing neurophysiological models with an accurate model of
a musculo-skeletal system, and then `closing the loop' by allowing the
movements of the virtual muscles to modulate sensory feedback to the
brain model, shortcomings in the constituent models would be revealed,
leading to new knowledge.
%
\rvw{We call this closed-loop approach \e{computational
neurobehaviour}, meaning a complete, behaving model, with attention
paid to the biological accuracy of each brain and biomechanical
sub-system. There already exist many closed-loop \e{robotic} systems which
receive sensory input from the world, process that input and generate
behaviour by activating motor
systems
\citep{yu_development_2004,fend_artificial_2004,pearson_whiskerbot:_2007}. We
now consider whether robotic systems which model biological
components \e{in hardware} could fall within our new category.
%
Using a number of examples, we will attempt to illustrate what we mean
by computational neurobehaviour. We'll consider which examples fall
into the new category and which are covered by other fields of
robotics or computational neuroscience.}

\rvw{\cite{pearson_whiskerbot:_2007} describes a wheeled robot which has a
biomimetic whisker sensory system, along with a biomimetic neural
system imitating the behaviour of the rat's sensory processing systems
and controlling the movement of the robot. \cite{fend_artificial_2004}
is a similar, wheeled, whiskered robot, with a repertoire of three
behaviours organised in a subsumption architecture. In both robots,
actions that are selected within the brain model drive a
non-biologically accurate wheel motor control algorithm to achieve
rotational and translational movements. Although both have
sensory and processing systems which are guided by biology, the
non-biological motor control stage prevents us from considering these
as being studies of computational neurobehaviour.}
%
\rvw{\cite{yu_development_2004} report on a biomimetic fish robot,
whose motor system closely resembles that of the real fish. The robot
is able to operate in a closed-loop mode, where sensory input is
provided to the non-biomimetic control algorithms from overhead
cameras, but its control system is also able to operate in open-loop
mode. Neither the control system, nor the sensory system are
biophysically accurate and we would not describe this study as
computational neurobehaviour. Nevertheless, the biophysically accurate
motor system could certainly form part of a computational
neurobehavioural study of swimming behaviour in the fish, if it were
combined with suitable sensory input and sensory processing models.}
%
\rvw{\cite{knips_neural_2017} is a report of a reach-and-grasp robot
arm controlled via a dynamic neural field brain model. The sensory
input for this system---its `eyes'---is a Microsoft Kinect sensor; it
also has somatosensory feedback from the fingers of the robot's
hand. The neural field `brain' controls the seven degrees of freedom
of the arm to carry out the reach-and-grasp action. While this robot
has closed-loop control and is clearly inspired by biology, it remains
a study of robotics and of the improvement of the control of the
robot's reach-and-grasp function, rather than a study which aims to
learn more about the biology of a primate arm. For this reason, we
would describe the study of \cite{knips_neural_2017} as embodied
robotics or neuro-robotics.}

\rvw{Modern programming platforms, often originating from the world
of computer gaming, make it relatively easy to model a virtual
environment. Consequently, an increasing number of studies into
robotic or neuro-mimetic control are carried out with virtual robots
operating within a virtual environment. \cite{arena_motor-skill_2017}
describes a robotic insect system based on the fly
species \e{Drosophila Melanogaster}. It has biomimetic insect legs
implemented in a virtual robot and a neuro-mimetic brain. Closing the
loop is a visual sensory input system which is able to determine the
distance between the robot and an obstacle and the obstacle's
height. The visual system is not described in detail and may not be
biologically modelled (much in the way that the visual processing
stream is not modelled in detail in the present work). Nevertheless,
this study may reasonably be described as compuational neurobehaviour;
the authors demonstrate that the virtual robot is able to learn to
climb obstacles in a realistic manner and suggest that the model may
be compared with experimental data from future Drosophila experiments
addressing obstacle climbing and learning.}
%
\rvw{\cite{nguyen_saccade_2014} and
\cite{thurat_biomimetic_2015} are two studies of the oculomotor system
which model sensory input, neural control and motor output. These
studies fall outside the remit of computational neurobehaviour only
because they omit to close the sensory
loop. \cite{dewolf_spiking_2016} describes a reach model comprising a
simplified virtual arm (with fewere degrees of freedom than a primate
arm), and a biologically inspired brain model. This model also omits
to close the sensory feedback loop and we consider it a traditional
computational neuroscience study.}

\rvw{We can now offer a definition of computational
neurobehaviour as: \e{The study of biological sensory-motor system
behaviour using biophysically accurate models of sensory input, brain
and motor sub-systems operating in a closed-loop}. The sub-system
models may be implemented in software or hardware, provided that they
attempt to reproduce and explain features of the biological
sub-system. We favour virtual biomechanics, for the ease with which
the biomechanical model can be modified and the flexibility of
computational modelling over hardware modelling.}

@@

% Reviewer 1's point 2.
\rvw{\bol{FIXME}. We should consider whether inaccuracies within one sub-system,
such as the musculo-skeletal model, may introduce errors that
propagate through the closed loop system and cannot be counteracted by
the nervous system part of the simulation.  My thoughts: You have to
do this alongside other research so that sub-systems are informed by
the best knowledge available.
%
How can you (or someone using this or related models)
exclude introducing (biomechanical) properties that are not present in
the biological system, or make sure to not miss critical biomechanical
properties that might help remedy some of the shortcomings of the
closed loop model?.}

% Reviewer 1's point 4.
\rvw{There are also experimental closed-loop approaches to
understanding sensorimotor control. \cite{ejaz_closed-loop_2013}
places a fly in a fixed position, and couples it with a free-to-move
robot. The sensory input collected by the robot is projected onto the
eyes of the fly, and activity from a selected neuron in the fly's
brain is used to drive a control system for the robot's
movements. This allows the experimenters to study the behaviour of the
fly's brain operating in a closed-loop condition that is more natural
than the open-loop condition that many other experimental techniques
mandate. The results from closed-loop experiments will undoubtedly
inform future neurobehavioural models.}

@@

\begin{figure}[htb!]
\begin{center}
\includegraphics[width=\textwidth]{./figures/ccg_model.png}
\end{center}
\textbf{\refstepcounter{figure}\label{fig:ccg_model} Figure \arabic{figure}.}
{ \bol{a) The macroscopic architecture of the \ccg~model.} The main
nuclei modelled as brain systems are: basal ganglia (BG), frontal eye
fields (FEF), thalamus (THAL) and superior colliculus (SC). The
retinal input is presented via non-biologically plausible retinal
populations. The loops through basal ganglia, which define the
architecture, are shown with coloured lines: the cortical loop
(through FEF and THAL) in green and the sub-cortical loop (through SC
and THAL) in blue. Connections with arrowheads indicate excitatory
connections, those with circles are inhibitory. A red border indicates
that the box represents a sub-system of two or more populations; a
black box indicates (at least, within the context of the model) a
single neural population. The BG box is expanded in: \bol{b) The basal
ganglia model component.}
%
This shows a basal ganglia comprising striatum (Str\_D1 \& Str\_D2),
subthalamic nucleus (STN), globus pallidum externum (GPe) and
substantia nigra reticulata (SNr). The model has three action channels
shown as black boxes within each blue population border. Three
channels of cortical input to the BG are also depicted. Red indicates
the activation level of a given channel, helping to illustrate the
selection mechanism. For example, the channel indicated by the
leftmost bar has a high salience (cortical input) and excites activity
in Str\_D1 which then inhibits the leftmost bar in SNr. The diffuse
projection from STN is equivalent to summing its projections
channel-wise, and then projecting the sum to all channels of its
target populations (the blue arrows indicate that all channels of GPe
and SNr are targeted by the connection). Dopaminergic modulation of
the inputs to the striatum are indicated by the blue circles labelled
`d' and the dotted lines. The SNr sends inhibitory output projections
to its targets. \bol{c) 2D Gaussian weights.} The `GaussianKernel'
connectivity pattern is based on the `in-plane displacement' between
the location of a neural element in one layer, and the location of a
target neural element in the target layer for the connection. The
potential weight of the connection is given by a 2D Gaussian function,
which is maximum for the target neuron which exactly corresponds to
the source neuron, and drops down for target neurons which are
horizontally displaced from the source neuron. A threshold is applied
to avoid a computationally expensive all-to-all connectivity (with
most of these connections having negligible weight values).  If the
weight is non-zero, then a connection is made from source to target,
otherwise no connection is made. \bol{d) Gaussian connectivity.} This
image shows connectivity (green rays) from two source neurons (in
Str\_D2, brown spheres) to target neurons (in GPe, blue spheres). The
circular connectivity pattern is seen. This does not show the weight
\e{values}, which reduce `towards the edge of the circle' and follow the
relationship shown in (c).}
\end{figure}
